### 2008-08-04 doc/storage_system/arc1-storage-documentation.tex
making security high priority

@@

The security is needed to do proper authorization of the users, and to manage access policies of files and collections. ARC has its own policy language, for each file and collection there will be a policy XML document stored as a metadata. The storage services will use the properties extracted from the communication channel and these policies to make authorization decisions. If the properties and the policies are present, the decision is actually made by the security framework of HED.

@@

@@

\section{Other plans} % (fold)

\subsection{Integrating third-party storage solutions} % (fold)
\label{sub:integrating_third_party_storage_solutions}

To intagrate existing files on a third-party storage to our namespace thus make them accessible through the interface of the ARC1 storage, we need a service which provides a common interface to the Bartender services, and hides the details of accessing the different third-party storages. It should translate the method calls, the \emph{get}s, \emph{put}s and \emph{remove}s and the \emph{ACL}\footnote{Access Control Lists, policies} modifications, and try to create transform metadata according to the data model of the ARC1 storage (Section~\ref{sub:data_model}). The files here would be referenced by a path which is local in the namespace of the third-party storage. The interface could be something like this:
\begin{description}
    \item[get(getRequest)] returns list of (\emph{requestID}, \emph{getResponseData})

@@

\end{description}
This interface has some methods similar to the Shepherd and some other methods similar to the Bartender.
% subsection integrating_third_party_storage_solutions (end)

\subsection{Security} % (fold)
\label{sub:security}

% subsection security (end)

% section other_plans (end)

>>>>

\section{Security} % (fold)
\label{sec:security}

The current version of the ARC1 storage system has no implemented solution for security issues. Designing and implementing a powerful, flexible, fine-grained solution for authentication and authorization is very important. Currently we have plans how to do that, and the design of the storage services makes it easy to integrate the chosen solution into the system.

For additional details, see Section~\ref{sec:plans_for_security}.

% section security (end)

@@

@@

\section{Plans for security} % (fold)
\label{sec:plans_for_security}

Security is needed to do proper authorization of the users, and to manage access policies of files and collections. ARC has its own policy language, for each file and collection there will be a policy XML document stored as a metadata. The storage services will use these policies and the properties extracted from the communication channel to make authorization decisions. If the properties and the policies are present, the decision will be actually made by the security framework of HED.

% section plans_for_security (end)

@@

\section{Integrating third-party storage solutions} % (fold)
\label{sec:integrating_third_party_storage_solutions}

To integrate existing files on a third-party storage system to our namespace thus make them accessible through the interface of the ARC1 storage, we need a service which provides a common interface to the Bartender services, and hides the details of accessing the different third-party storages. It should translate the method calls, the \emph{get}s, \emph{put}s and \emph{remove}s and the \emph{ACL}\footnote{Access Control Lists, policies} modifications, and try to create transform metadata according to the data model of the ARC1 storage (Section~\ref{sub:data_model}). The files here would be referenced by a path which is local in the namespace of the third-party storage. The interface could be something like this:
\begin{description}
    \item[get(getRequest)] returns list of (\emph{requestID}, \emph{getResponseData})

@@

\end{description}
This interface has some methods similar to the Shepherd and some other methods similar to the Bartender.
% section integrating_third_party_storage_solutions (end)
